Appendix A: Feature comparison between `Distance` and other packages

### 2016-05-15 paper.Rmd
quotes when using data()

The minke whale data follows the "flatfile" format given in the last bullet point:
```{r minke-data-head, message=FALSE}
library("Distance")
data(minke)
head(minke)
```
Whereas the amakihi data lacks effort and stratum data:
```{r amakihi-data-head}
data(amakihi)
head(amakihi)
```

>>>>

The minke whale data follows the "flatfile" format given in the last bullet point:
```{r minke-data-head, message=FALSE}
library("Distance")
data("minke")
head(minke)
```
Whereas the amakihi data lacks effort and stratum data:
```{r amakihi-data-head}
data("amakihi")
head(amakihi)
```
